---
title: "ThesisSurveyCluster"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output:
  pagedown::html_paged:
    css: www/my_css.css
    number_sections: no
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, class.source = "watch-out", options(scipen=999), out.width = "65%", warning = FALSE, comment = "") 
source("www/init.R")
source("www/Table_Design.R")
```

```{r, echo=FALSE}
htmltools::img(
  src = knitr::image_uri(file.path("www/BSM_Logo.png")), 
  alt = 'logo', 
  style = 'position:absolute; top:0; right:5px; padding:10px; width:200px'
)
```

# Clustering & Correspondence analysis

**Steps:**
1. Decide which columns to use, decide coding to get homogeneous for clustering
2. Clustering
3. Correspondence analysis, bring in demographics. 
4. Individual cluster analysis - sub-sample


## Loading dataset

```{r data, echo=FALSE, include=FALSE}
data <- read_excel("Main doc survey.xlsx")
attach(data)

dani <- c( "#ffa500", "#34495E", "#69b3a2", "#ffd561", "#ee5c42", "#DAF7A6", "#C8A2C8", "#5c3170", "#990000", "#C70039", "#34495E", "#909497")

pal9 <- jcolors("pal9")
```

[Reference to Methodology applied.](https://towardsdatascience.com/k-means-clustering-algorithm-applications-evaluation-methods-and-drawbacks-aa03e644b48a "Reference to Methodology applied."){.uri}

### Transforming variables

Primarily several multi-option variables are removed from the dataset. Next dummies are created for the categorical variables.

*If the option is not selected, the answer corresponds with 0.\
If the option has been selected, the answer corresponds with 1.*

```{r}
data <- separate(
  data,
  Criteria_Type_Coffee,
  into = c("Criteria_A", "Criteria_B"),
  sep = "([,])",
  remove = TRUE,
  convert = FALSE,
  extra = "drop",
  fill = "right",
)

data <- separate(
  data,
  Subscription_Not_Likely,
  into = c("Subscription_A", "Subscription_B"),
  sep = "([,])",
  remove = TRUE,
  convert = FALSE,
  extra = "drop",
  fill = "right",
)

data <- separate(
  data,
  "Supermarket_Negative_ Reasons",
  into = c("Supermarket_NO_A", "Supermarket_NO_B"),
  sep = "([,])",
  remove = TRUE,
  convert = FALSE,
  extra = "drop",
  fill = "right",
)

data <- separate(
  data,
  "Supermarket_Positive_ Reasons",
  into = c("Supermarket_YES_A", "Supermarket_YES_B"),
  sep = "([,])",
  remove = TRUE,
  convert = FALSE,
  extra = "drop",
  fill = "right",
)
```

### One-hot Encoding

```{r, echo=FALSE}
data <- data[,-match(c("Language", "Participant", "Home", "Occupation", "Gender", "Education", "AgeCategory", "Criteria_B", "Subscription_B", "Supermarket_NO_B", "Supermarket_YES_B"),names(data))]

dataf <- dummy_cols(data, select_columns = c("Criteria_A", "Subscription_A", "Supermarket_NO_A", "Supermarket_YES_A", "Machine", "BrandChange", "PurchaseLocation",  "Frequency_Specialty"), remove_selected_columns = TRUE, ignore_na = TRUE)
```

Separate the second, responses to 0.1.  Do not categorize on demographics together with the preferences. Everything to do with coffee has to be in cluster analysis.

```{r}
# Prepare Data
Orgdata <- na.omit(dataf) # listwise deletion of missing
stdata <- scale(Orgdata[,c(1:12)]) # standardize variables
NewData <- cbind(stdata, Orgdata[,c(13:64)])
```


## Clustering including categorical variables

The next step is to remove this missing variables (NA), standardize the numerical variables and combine to make the new data table to be used for the cluster analysis.

### Finding optimal number of clusters

Based on the graph below, I have decided to use 4 numbers of cluster.

```{r}
NewData <- na.omit(NewData)

distance <- get_dist(NewData)
graph <- fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
fviz_nbclust(NewData, kmeans, method = "wss")
```

## Performing clusters

```{r}
set.seed(1234)

# K-Means Cluster Analysis
fit <- kmeans(na.omit(NewData), centers = 4, nstart = 50) #4 cluster solution
fit2 <- kmeans(na.omit(NewData), centers = 3, nstart = 50) #3 cluster solution
fit3 <- kmeans(na.omit(NewData), centers = 2, nstart = 50) #2 cluster solution
fit4 <- kmeans(na.omit(NewData), centers = 1, nstart = 50) #1 cluster solution
```


**Getting cluster means:**

```{r}
fitMeans <- aggregate(Orgdata,
  by=list(cluster = fit$cluster),
  FUN=mean,
  )
fitMeans <- round(fitMeans)
my_table(fitMeans)
```

**Adding cluster classification to the original data set**

```{r}
# append cluster assignment
mydata <- data.frame(na.omit(NewData), fit$cluster)
```


**Summary fit k=4**

```{r}
print(fit)
```


**Within sum of squares:**

```{r}
print(fit$withinss)
print(fit2$withinss)
print(fit3$withinss)
```

**Creating new data sets for each cluster group**

```{r}
clustereddata <- cbind(data, Cluster = fit$cluster)

cluster1 <- subset(clustereddata, Cluster=='1')
cluster2 <- subset(clustereddata, Cluster=='2')
cluster3 <- subset(clustereddata, Cluster=='3')
cluster4 <- subset(clustereddata, Cluster=='4')
```


### Visualizing clusters

Provides ggplot2-based elegant visualization of partitioning methods including kmeans [stats package]; pam, clara and fanny [cluster package]; dbscan [fpc package]; Mclust [mclust package]; HCPC [FactoMineR]; hkmeans [factoextra]. Observations are represented by points in the plot, using principal components if ncol(data) > 2. An ellipse is drawn around each cluster.

```{r}
fviz_cluster(fit, geom = "point", data = stdata, outlier.color = "black", palette = dani) + ggtitle("k = 4")

p1 <- fviz_cluster(fit, geom = "point", data = stdata, outlier.color = "black", palette = dani) + ggtitle("k = 4")

p2 <- fviz_cluster(fit2, geom = "point", data = stdata, outlier.color = "black", palette = dani) + ggtitle("k = 3")

p3 <- fviz_cluster(fit3, geom = "point", data = stdata, outlier.color = "black", palette = dani) + ggtitle("k = 2")

p4 <- fviz_cluster(fit4, geom = "point", data = stdata, outlier.color = "black", palette = dani) + ggtitle("k = 1")

grid.arrange(p1, p2, p3, p4, nrow = 2)
```


```{r}
Subdata <- data.frame("Money Coffee" = clustereddata$MoneyCoffee, "Money Groceries" = clustereddata$MoneyGroceries, "Amount Out per month" = clustereddata$AmountOutMonth, 'Amount per week' = clustereddata$AmountWeek)

par(mar=c(2,4,3,1), font.lab=2, mfrow=c(1,4), mgp=c(2,0.7,0))
for(j in 1:4) boxplot(Subdata[,j] ~ clustereddata$Cluster, main=colnames(Subdata)[j], 
                      col=c("#34495E", "#69b3a2"), ylab="%")
```

```{r}
Subdata <- data.frame("Knowledge Coffee" = clustereddata$KnowledgeCoffee, 'Subscription Likeliness' = clustereddata$Subscription_Likely, "App Likeliness" = clustereddata$App_Likely)

par(mar=c(2,4,3,1), font.lab=2, mfrow=c(1,3), mgp=c(2,0.7,0))
for(j in 1:3) boxplot(Subdata[,j] ~ clustereddata$Cluster, main=colnames(Subdata)[j], 
                      col=c("#34495E", "#69b3a2"), ylab="%")
```

```{r}
Subdata <- data.frame(Price = clustereddata$Purchase_Price, Sustainability = clustereddata$Purchase_Sustainability, Certification = clustereddata$Purchase_Certificate, Fairtrade = clustereddata$Purchase_Fairtrade, Packaging = clustereddata$Purchase_Packaging)

par(mar=c(2,4,3,1), font.lab=2, mfrow=c(1,5), mgp=c(2,0.7,0))
for(j in 1:5) boxplot(Subdata[,j] ~ clustereddata$Cluster, main=colnames(Subdata)[j], 
                      col=c("#34495E", "#69b3a2"), ylab="%")
```

## Principal component analysis

```{r}
#PCA(stdata, scale.unit = TRUE, ncp = 5, graph = TRUE)
```

```{r}
DK2.dist <- dist(NewData)
DK1.mds <- cmdscale(DK2.dist, eig=TRUE)

plot(DK1.mds$points, asp=1, main="Distances",
     xlab="MDS dimension 1", ylab="MDS dimension 2", type="p", col="#69b3a2", font=2, cex=0.8)

DK1.mds$GOF
```

```{r}
library(factoextra)
fviz_eig(DK2.PCA, addlabels = TRUE, ylim = c(0, 50))
```


```{r}
#require(easyCODA)

DK2.PCA <- PCA(as.matrix(NewData))
PLOT.PCA(DK2.PCA, map="asymmetric")
summary(DK2.PCA)

DK.PCA <- PCA(NewData)
par(mar=c(4.2,4,4,1), font.lab=2, cex.axis=0.8, mgp=c(2.5,0.7,0))
PLOT.PCA(DK.PCA, map="asymmetric", rescale=0.05, main="PCA with chi-square standardization")
```


```{r}
library(FactoMineR)

DK2.PCA <- PCA(as.matrix(stdata))

clusters <- as.factor(fit$cluster)

fviz_pca_ind(DK2.PCA,
             geom.ind = "point", # show points only (nbut not "text")
             col.ind = clusters, # color by groups
             palette = c("#ffa500", "#34495E", "#69b3a2", "#ffd561"),
             addEllipses = TRUE, # Concentration ellipses
             legend.title = "Clusters"
             )
```

### Biplots

```{r}
fviz_pca_biplot(DK2.PCA, 
                col.ind = clusters, palette = c("#ffa500", "#34495E", "#69b3a2", "#ffd561"),
                addEllipses = TRUE, label = "var",
                col.var = "black", repel = TRUE,
                legend.title = "Clusters") 
```

**Sub setted data**

```{r}
Subdata <- data.frame(Price = clustereddata$Purchase_Price, Sustainability = clustereddata$Purchase_Sustainability, Certification = clustereddata$Purchase_Certificate, Fairtrade = clustereddata$Purchase_Fairtrade, Packaging = clustereddata$Purchase_Packaging)

Subdata.PCA <- PCA(as.matrix(Subdata))

fviz_pca_biplot(Subdata.PCA, 
                col.ind = clusters, palette = c("#ffa500", "#34495E", "#69b3a2", "#ffd561"),
                addEllipses = TRUE, label = "var",
                col.var = "black", repel = TRUE,
                legend.title = "Clusters") 
```


```{r, echo=FALSE, include=FALSE}
require(rgl)
DK2.dist <- dist(NewData)
DK.mds <- cmdscale(DK2.dist, eig=TRUE, k=4)
plot3d(DK.mds$points[,c(1,3,2)], xlab="dim1", ylab="dim3", zlab="dim2", type="p")

play3d(spin3d(c(0,0,1)), duration=12)

#rgl.snapshot("view3D.png")
```




```{r}
DK2.PCA <- PCA(NewData, graph = FALSE)

# Contributions of variables to PC1
fviz_contrib(DK2.PCA, choice = "var", axes = 1, top = 10)
# Contributions of variables to PC2
fviz_contrib(DK2.PCA, choice = "var", axes = 2, top = 10)
```

```{r}
grp <- as.factor(fit$cluster)
# Color variables by groups
fviz_pca_var(DK2.PCA, col.var = grp, 
             palette = c("#ffa500", "#34495E", "#69b3a2", "#ffd561"),
             legend.title = "Cluster")
```

```{r}
sil <- silhouette(fit$cluster, dist(NewData))
fviz_silhouette(sil)
```

## Correspondence Analysis

Cross tabulations, two categorical variables


\newpage

### The clusters individual results

```{r}
Results <- as.data.table(aggregate(na.omit(Orgdata[,1:5]), by=list(cluster=fit$cluster), mean), by = round)

Results_Round <- round(Results)
my_table(Results_Round)
```

```{r}
Results <- as.data.table(aggregate(na.omit(Orgdata[,6:10]), by=list(cluster=fit$cluster), mean), by = round)

Results_Round <- round(Results,1)

my_table(Results_Round)
```

```{r}
Results <- as.data.table(aggregate(na.omit(Orgdata[,11:12]), by=list(cluster=fit$cluster), mean), by = round)

Results_Round <- round(Results,1)

my_table(Results_Round)
```

```{r}
Results <- as.data.table(aggregate(na.omit(Orgdata[,13:20]), by=list(cluster=fit$cluster), mean), by = round)

Results_Round <- round(Results)
my_table(Results_Round)
```

```{r}
agetable1 <- as.data.table(table(cluster1$AgeCategory))
colnames(agetable1) <- c("Age", "Frequency")
  
agetable2 <- as.data.table(table(cluster2$AgeCategory) )
colnames(agetable2) <- c("Age", "Frequency")

agetable3 <- as.data.table(table(cluster3$AgeCategory) )
colnames(agetable3) <- c("Age", "Frequency")

agetable4 <- as.data.table(table(cluster4$AgeCategory) )
colnames(agetable4) <- c("Age", "Frequency")

my_table(agetable1)
my_table(agetable2)
my_table(agetable3)
my_table(agetable4)
```

```{r}
table1 <- as.data.table(table(cluster1$Machine))
colnames(table1) <- c("Machine", "Frequency")
  
table2 <- as.data.table(table(cluster2$Machine) )
colnames(table2) <- c("Machine", "Frequency")

table3 <- as.data.table(table(cluster3$Machine) )
colnames(table3) <- c("Machine", "Frequency")

table4 <- as.data.table(table(cluster4$Machine) )
colnames(table4) <- c("Machine", "Frequency")

my_table(table1)
my_table(table2)
my_table(table3)
my_table(table4)
```

```{r}
table1 <- as.data.table(table(cluster1$PurchaseLocation))
colnames(table1) <- c("PurchaseLocation", "Frequency")
  
table2 <- as.data.table(table(cluster2$PurchaseLocation) )
colnames(table2) <- c("PurchaseLocation", "Frequency")

table3 <- as.data.table(table(cluster3$PurchaseLocation) )
colnames(table3) <- c("PurchaseLocation", "Frequency")

table4 <- as.data.table(table(cluster4$PurchaseLocation) )
colnames(table4) <- c("PurchaseLocation", "Frequency")

my_table(table1)
my_table(table2)
my_table(table3)
my_table(table4)
```


```{r}
table1 <- as.data.table(table(cluster1$Frequency_Specialty))
colnames(table1) <- c("PurchaseLocation", "Frequency")
  
table2 <- as.data.table(table(cluster2$Frequency_Specialty) )
colnames(table2) <- c("Frequency_Specialty", "Frequency")

table3 <- as.data.table(table(cluster3$Frequency_Specialty) )
colnames(table3) <- c("Frequency_Specialty", "Frequency")

table4 <- as.data.table(table(cluster4$Frequency_Specialty) )
colnames(table4) <- c("Frequency_Specialty", "Frequency")

my_table(table1)
my_table(table2)
my_table(table3)
my_table(table4)
```

```{r}
Results <- as.data.table(aggregate(na.omit(Orgdata[,35:40]), by=list(cluster=fit$cluster), mean), by = round)

Results_Round <- round(Results)
my_table(Results_Round)
```

***

## References


<https://towardsdatascience.com/clustering-analysis-in-r-using-k-means-73eca4fb7967>

<http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/112-pca-principal-component-analysis-essentials/> 


